ActiveCA: an open data product on active transportation episodes in Canada

### 2024-11-13 paper/Manuscript-Data-Package.Rmd
Revisions to package configuration and reproducibility

# Pivot data for the table layout
wide_data <- episodes_stats_before %>%
  pivot_wider(
    id_cols = c(dest_label, MODE),
    names_from = YEAR,
    values_from = c(min, median, max, Percentage)
  )  %>% 
  arrange(dest_label, MODE, desc(Percentage_1998))

@@

# Filter for walking and cycling trips, selected years, and duration <= 90
episodes_stats_after <- gss_episodes_renamed %>%
  filter(YEAR > 2000) %>%
  group_by(YEAR, dest_label, MODE) %>%
  summarise(
    count = n(),
    min = min(DURATION),
    median = median(DURATION),
    max = max(DURATION),
    .groups = "drop"
  )

@@

# Pivot data for the table layout
wide_data <- episodes_stats_after %>%
  pivot_wider(
    id_cols = c(dest_label, MODE),
    names_from = YEAR,
    values_from = c(min, median, max, Percentage)
  ) %>%
 dplyr::select(
    dest_label, MODE,
    min_2005, median_2005, max_2005, Percentage_2005,
    min_2010, median_2010, max_2010, Percentage_2010,
    min_2015, median_2015, max_2015, Percentage_2015
  ) %>% 
  arrange(dest_label, MODE, desc(Percentage_2015)) %>%
  group_by(MODE) %>%
  mutate(MODE = if_else(row_number() == 2, as.character(MODE), "")) %>%
  ungroup()

>>>>

# Pivot data for the table layout
wide_data <- episodes_stats_before %>%
  pivot_wider(
    id_cols = c(dest_label, MODE),
    names_from = YEAR,
    values_from = c(min, median, max, Percentage)
  )  %>% 
  arrange(MODE, dest_label, desc(Percentage_1998))

@@

episodes_stats_after <- gss_episodes_renamed %>%
  filter(YEAR > 2000) %>%
  group_by(YEAR, dest_label, MODE) %>%
  summarise(
    count = n(),
    min = min(DURATION),
    median = median(DURATION),
    max = max(DURATION),
    .groups = "drop"
  )

@@

# Pivot data for the table layout
wide_data <- episodes_stats_after %>%
  pivot_wider(
    id_cols = c(dest_label, MODE),
    names_from = YEAR,
    values_from = c(min, median, max, Percentage)
  ) %>%
 dplyr::select(
    dest_label, MODE,
    min_2005, median_2005, max_2005, Percentage_2005,
    min_2010, median_2010, max_2010, Percentage_2010,
    min_2015, median_2015, max_2015, Percentage_2015
  ) %>% 
  arrange(MODE, dest_label, desc(Percentage_2015)) %>%
   group_by(MODE) %>%
   mutate(MODE = if_else(row_number() == 2, as.character(MODE), "")) %>%
   ungroup()
